Universal Anonymous Signatures

### 2022-10-06 prism-backend/research/gsac/app-related-extra.tex
Fixed some flaws. Still doing passes for minor checks.
Minor edits.

We give a simple definition for a Delegatable Anonymous Credentials (DAC)
scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
our simple scheme built from \CUASGenInt does not ensure privacy of the
delegation chain, which means that only actions by users with the same
delegation chain are indistinguishable -- this can make sense, for instance,
for organisations composed by many members. Delegation chain privacy could be
achieved by making \feval output projective proofs like in \cite{bcc+09} (or,
to some extent, building on \CUASGenHideIss rather than on \CUASGen), but we
leave that out of scope for brevity. Our simple scheme
does, however, ensure that a (not top-level) issuer can only delegate attributes
contained in a credential it owns. Also, for simplicity, we restrict to the case
of using one credential per signature/interactive credential presentation, and
assume that all parties use the same opener and \finsp function.
%
The syntax is thus defined almost as in \secref{ssec:related-models-ac},
i.e., we have a $Setup$ algorithm, and $\langle Obtain,Issue\rangle$
and $\langle Show,Verify \rangle$ interactive protocols; but we do not have
$IssKeyGen$, as now, as in \cite{bcc+09} (and our \UAS model), issuers collapse
with users -- instead, we have an $KG$ and $ISet$ algorithms, with the same
meaning as in \UAS.
%
In the model for this setting, since there are multiple issuers, in addition
to the oracles in \secref{ssec:related-models-ac}, we use $HI$ and $CI$ oracles,
for creating honest and corrupt issuers, which can be simulated via \HUGEN,
\CUGEN, \ISET and \ICORR in our \UAS model.
%
The issuance and sign anonymity properties are direct, constraining the
adversary to output challenge credentials and signatures with the same
delegation chain. For unforgeability, we still require that no adversary can
authenticate using a set of attributes that have not been issued to a corrupt
user. In addition, we require that for any successful authentication using a
level-$l$ credential, we can extract a chain of credentials of length $l$ such
that each level-$i$ credential can be used successfully to authenticate the
level-$(i+1)$ credential, all the way down to the level-$l$ credential, and the
attributes revealed in the level-$l$ authentication are contained in all the
credentials up the chain. For this extraction, we assume in the model the
existence of a helper function $(\ipk_0,\lbrace (\ipk_i,\cred_i)
\rbrace_{i\in[1,l]}) \gets \helper{ExtractChain}(\utrans)$ that outputs a
sequence of public keys and credentials from the root issuer $\ipk_0$ to the
actual credential used to sign $(\ipk_l,\cred_l)$.

@@

\begin{align}
  & \fissue^{l,D}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
    \pcreturn \attrs_1 = l+1 \land \cattrs \subseteq D \nonumber \\
  & \feval^{l,\dattrs}(\cdot,(\cid,\attrs),\cdot) \coloneqq
    \pcreturn((\attrs_1,\lbrace\attrs_i\rbrace_{i\in\dattrs}),\ast)
    \label{eq:funcs-dac}
\end{align}

@@

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to \oracle{HU},\oracle{CU},\oracle{Obtain},
  \oracle{Show},\oracle{IssLoR}, \advB redirects to the \CUASGenInt oracles
  \HUGEN,\CUGEN,\OBTAIN,\SIGN,\OBTCHALb, respectively. \oracle{HI} (resp.
  \oracle{CI}) is simulated by calling \HUGEN (resp. \CUGEN) and \ISET
  sequentially and for the same \uid, plus a call to \SIGN in the case of
  honest issuers of level $l>0$, to generate the signature \Sig that the
  (honest) issuer has to publish.
  %
  If \adv~wins in its issuance anonymity game, then so does \advB with the same
  probability, as the simulation is perfect.
  % 
  \qed
\end{proof}

@@

\begin{proof}
  Given \adv~ against signature anonymity of \CUASDAC as defined in
  $\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$, we build an adversary \advB against
  signature anonymity of \CUASGenInt.
  %
  \adv's oracles are simulated as in the proof for issuance anonymity of
  \CUASDAC -- in this case, \adv's \oracle{SigLoR} oracle corresponds to \advB's
  \CHALb. Again, the simulation is perfect, and whenever \adv~wins its
  $\Exp^{sig-anon-b}$ game, so does \advB.
  % 
  \qed
\end{proof}

@@

\begin{proof}
  First, we define the $ExtractChain(\utrans)$ function for our construction.
  Note that \utrans is a tuple $(r,\Sig)$\footnote{This follows for the approach
    to transform non-interactive signature and verification in \UAS to
    interactive presentations, as described in \secref{ssec:variants}.}, where
  $r$ is a fresh random number specified by the adversary,
  and \Sig is a \CUASGen signature over $r$. Thus, $ExtractChain$ leverages
  \ExtractSign from \CUASGen (see \secref{ssec:security-uas}) to get the
  credential and associated \ipk used to produce \Sig. Note that, for this
  \ipk (of level $n$), $\ipk = \ipk_{n-1}$ in $\Exp^{forge}_{\adv,dac}$. In
  \CUASDAC, we can leverage $\ipk_{n-1}$ to fetch from the public list a
  signature $\Sig_{n-1}$ generated by the issuer owner of $\ipk_{n-1}$. Again,
  we apply \ExtractSign from \CUASGen, to get the credential one layer up in the
  chain. \helper{ExtractChain} repeats this step, until reaching the top level
  credential, issued by $\ipk_0$.

  From the previous, the same reasoning as in \thmref{thm:forge-cuasac} applies
  to an adversary \adv~winning at line 5 of $\Exp^{forge}_{\adv,dac}$. Next,
  suppose that from \utrans, $ExtractChain$ outputs at line 6 a
  delegation chain that makes \adv~win at line 9. This means that an
  uncorrupted issuer at position $i-1$ of the chain did not own a credential
  containing $D'$, but the issuer at position $i$ does. Then, either of the
  following must happen:

>>>>

We give a simple definition for a Delegatable Anonymous Credentials (DAC)
scheme, extending \cite{fhs19} and inspired by \cite{bcc+09}. Unlike the latter,
our simple scheme built from \CUASGenInt does not ensure privacy of the
delegation chain, which means that only actions by users with the same
delegation chain are indistinguishable -- this can make sense, for instance,
for organisations composed by many members. Delegation chain privacy could be
achieved by making \feval output projective proofs like in \cite{bcc+09} (or,
to some extent, building on \CUASGenHideIss rather than on \CUASGen), but we
leave that out of scope for brevity. Our simple scheme
does, however, ensure that a (not top-level) issuer can only delegate attributes
contained in a credential it owns. Also, for simplicity, we restrict to the case
of using one credential per signature/interactive credential presentation, and
assume that all parties use the same opener and \finsp function.
%
The syntax is thus defined almost as in \secref{ssec:related-models-ac},
i.e., we have a $Setup$ algorithm, and $\langle Obtain,Issue\rangle$
and $\langle Show,Verify \rangle$ interactive protocols; but we do not have
$IssKeyGen$, as now, as in \cite{bcc+09} (and our \UAS model), issuers collapse
with users -- instead, we have an $KG$ and $ISet$ algorithms, with the same
meaning as in \UAS.
%
In the model for this setting, since there are multiple issuers, in addition
to the oracles in \secref{ssec:related-models-ac}, we use \oracle{HI} and
\oracle{CI} oracles,
for creating honest and corrupt issuers, which can be simulated via \HUGEN,
\CUGEN, \ISET and \ICORR in our \UAS model.
%
The issuance and sign anonymity properties are direct, constraining the
adversary to output challenge credentials and signatures with the same
delegation chain. For unforgeability, we still require that no adversary can
authenticate using a set of attributes that have not been issued to a corrupt
user. In addition, we require that for any successful authentication using a
level-$l$ credential, we can extract a chain of credentials of length $l$ such
that each level-$i$ credential can be used successfully to authenticate the
level-$(i+1)$ credential, all the way down to the level-$l$ credential, and the
attributes revealed in the level-$l$ authentication are contained in all the
credentials up the chain. For this extraction, we assume in the model the
existence of a helper function $(\ipk_0,\lbrace (\ipk_i,\cred_i)
\rbrace_{i\in[1,l]}) \gets \helper{ExtractChain}(\utrans)$ that outputs a
sequence of public keys and credentials from the root issuer $\ipk_0$ to the
actual credential used to sign $(\ipk_l,\cred_l)$.

@@

\begin{align}
  & \fissue^{l,D}(\cdot,\attrs,(\cid,\cattrs)) \coloneqq
    \pcreturn \cattrs_1 = l \land \attrs_1 = l+1
    \land \cattrs \subseteq D \land \attrs_{[2..n]} \subseteq \cattrs \nonumber \\
  & \feval^{l,\dattrs}(\cdot,(\cid,\attrs),\cdot) \coloneqq
    \pcreturn((\attrs_1,\lbrace\attrs_i\rbrace_{i\in\dattrs}),\ast)
    \label{eq:funcs-dac}
\end{align}

@@

  To simulate oracle calls by \adv, \advB simply redirects to its corresponding
  oracle, i.e.: for calls to \oracle{HU},\oracle{CU},\oracle{Obtain},
  \oracle{Show},\oracle{IssLoR}, \advB redirects to the \CUASGenInt oracles
  \HUGEN,\CUGEN,\OBTAIN,\SIGN,\OBTCHALb, respectively. \oracle{HI} (resp.
  \oracle{CI}) is simulated by calling \HUGEN (resp. \CUGEN) and \ISET
  sequentially and for the same \uid, plus a call to \SIGN in the case of
  honest issuers of level $l>0$, to generate the signature \Sig that the
  (honest) issuer has to publish.
  %
  Note that the issuance anonymity game for DAC is essentially the same as that
  for \UAS, with the exception that -- to avoid trivial wins -- in the DAC game
  we do not allow credentials with different delegation chains to be used
  simultaneously in the challenge oracle.
  %
  Thus, if \adv~wins in its game, so does \advB.
  % 
  \qed
\end{proof}

@@

\begin{proof}
  Given \adv~against signature anonymity of \CUASDAC as defined in
  $\Exp^{sig-anon-b}_{\adv,dac}(1^\secpar)$, we build an adversary \advB against
  signature anonymity of \CUASGenInt.
  %
  \adv's oracles are simulated as in the proof for issuance anonymity of
  \CUASDAC -- in this case, \adv's \oracle{SigLoR} oracle corresponds to \advB's
  \CHALb.
  %
  Again, the game is the same as for \UAS, only conditioned on the challenge
  signatures being produced from credentials with the same delegation chain.
  Thus, whenever \adv~wins its $\Exp^{sig-anon-b}$ game, so does \advB.
  % 
  \qed
\end{proof}

@@

\begin{proof}
  First, we define the $\helper{ExtractChain}(\utrans)$ function for our
  construction. Note that \utrans is a tuple $(r,\Sig)$\footnote{This follows
    for the approach
    to transform non-interactive signature and verification in \UAS to
    interactive presentations, as described in \secref{ssec:variants}.}, where
  $r$ is a fresh random number specified by the adversary, and \Sig is a
  \CUASGen signature over $r$. Thus, \helper{ExtractChain} leverages
  \ExtractSign from \CUASGen (see \secref{ssec:security-uas}) to get the
  credential and associated \ipk used to produce \Sig. Note that, for this
  \ipk (of level $n$), $\ipk = \ipk_{n-1}$ in $\Exp^{forge}_{\adv,dac}$. In
  \CUASDAC, we can leverage $\ipk_{n-1}$ to fetch from the public list a
  signature $\Sig_{n-1}$ generated by the issuer owner of $\ipk_{n-1}$. Again,
  we apply \ExtractSign from \CUASGen, to get the credential one layer up in the
  chain. \helper{ExtractChain} repeats this step, until reaching the top level
  credential, issued by $\ipk_0$.

  From the previous, the same reasoning as in \thmref{thm:forge-cuasac} applies
  to an adversary \adv~winning at line 5 of $\Exp^{forge}_{\adv,dac}$. Next,
  suppose that from \utrans, \helper{ExtractChain} outputs at line 6 a
  delegation chain that makes \adv~win at line 9. This means that an
  uncorrupted issuer at position $i-1$ of the chain did not own a credential
  containing $D'$, but the issuer at position $i$ does. Then, either of the
  following must happen:

### 2022-10-06 prism-backend/research/gsac/app-uas-proofs.tex
Minor edits.

  We start from $G_0=\ExpSigAnonb$.  %
  From $G_0$, we consider $G^0_0 = \ExpSigAnonz$. The challenge sent to the
  adversary is $(\csig_0,\yeval) \gets \Sign(\PRVUK[\cuid_0],\PUBOK[\oid],
  \CRED[\scid_0],\msg,\feval)$, where $\csig_0 = (\pi_0,\cinsp)$, with
  $\pi_0 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},(\msg,\feval,\yeval,
  \cinsp,\lbrace\PUBIK[\scid_{i,0}]\rbrace_{i\in[n]},\PUBOK[\oid]),
  (\PUBUK[\cuid_0],\PRVUK[\cuid_0],\lbrace (\scid_{i,0},\attrs_{i,0},
  \CRED[\scid_{i,0}]) \rbrace_{i\in[n]},\yeval^1,\yinsp,r,r'))$, and $\cinsp =
  \EEnc(\PUBOK[\oid],\yinsp;r')$, for some random $r,r'$ and $n \ge 0$.
  % 
  Further, we build $G_1^0$ from $G_0^0$ by simulating the proof $\pi_0$. That
  is, in $G_1^0$, $\csig_0 = (\pi_0^s,\ceval,\cinsp)$, where $\pi^s_0 =
  \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
  \cinsp,\lbrace\PUBIK[\scid_{i,0}]\rbrace_{i\in[n]},\PUBOK[\oid]))$. By
  zero-knowledgeness of $\NIZK^{\Sign}$, $G_1^0$ is indistinguishable from
  $G_0^0$.

  Similarly, we consider $G_0^1$ and $G_1^1$. That is, $G_0^1 = \ExpSigAnono$,
  where the challenge
  sent to the adversary is $(\csig_1,\yeval) \gets \Sign(\PRVUK[\cuid_1],
  \PUBOK[\oid],\CRED[\scid_1],\msg,\feval)$, where $\csig_1 = (\pi_1,
  \cinsp)$, with $\pi_1 = \NIZKProve^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},
  (\msg,\feval,\yeval,
  \cinsp,\lbrace\PUBIK[\scid_{i,1}]\rbrace_{i\in[n]},\PUBOK[\oid]),
  (\PUBUK[\cuid_1],\PRVUK[\cuid_1],\lbrace (\scid_{i,1},\attrs_{i,1},
  \CRED[\scid_{i,1}]) \rbrace_{i\in[n]},\yeval^1,\yinsp,r,r'))$, and
  $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$, for random $r,r'$ and $n \ge 0$. As
  before, build $G_1^1$ from $G_0^1$, simulating $\pi_1$. That is, in $G_1^1$,
  $\csig_1 = (\pi_1^s,\ceval,\cinsp)$, where $\pi^s_1 =
  \NIZKSim^{\NIZKRel_{\Sign}}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
  \cinsp,\lbrace\PUBIK[\scid_{i,1}]\rbrace_{i\in[n]},\PUBOK[\oid]))$. Again, by
  zero-knowledge of $\NIZK^{\Sign}$, $G_1^1$ is
  indistinguishable from $G_0^1$.

@@

  Next, we prove that, after zero-knowledge and simulation extractability of the
  NIZK for \RelSig, and blindness of \SBCM, no credential from an honest user
  can be extracted from the signature output by \adv, except with negligible
  probability.
  %
  The crucial observation is that, as in \cite{cl06} \CUASGen's \Sign algorithm
  produces a signature of knowledge for the relation defined by \RelSig
  That is, given $(x,w) \in \NIZKRel^{\Sign}$, one can compare $x$ and $w$ to
  the public and private key of a signature algorithm, respectively. In \RelSig,
  $(\upk,\usk,\lbrace (\cid_i,\attrs_i,
  \cred_i)\rbrace_{i\in[n]},\yeval^1,\yinsp,r,r')$ is the private key ($w$), and
  $(\msg,\feval,\yeval^0,\cinsp,\lbrace \ipk_i \rbrace_{i\in[n]},\ek)$ is the
  public key ($x$).
  %
  From this, we prove that an adversary has only negligible probability to forge
  a signature as originating from an honest user without calling the \SIGN
  oracle. The strategy is similar to that in \cite[Theorem 2.1]{cl06}.

>>>>

  We start from $G_0=\ExpSigAnonb$.  %
  From $G_0$, we consider $G^0_0 = \ExpSigAnonz$. The challenge sent to the
  adversary is $(\csig_0,\yeval) \gets \Sign(\PRVUK[\cuid_0],\PUBOK[\oid],
  \CRED[\scid_0],\msg,\feval)$, where $\csig_0 = (\pi_0,\cinsp)$, with
  $\pi_0 = \NIZKProve^{\RelSig}(\NIZKcrs_{\Sign},(\msg,\feval,\yeval,
  \cinsp,\lbrace\PUBIK[\scid_{i,0}]\rbrace_{i\in[n]},\PUBOK[\oid]),
  (\PUBUK[\cuid_0],\PRVUK[\cuid_0],\lbrace (\scid_{i,0},\attrs_{i,0},
  \CRED[\scid_{i,0}]) \rbrace_{i\in[n]},\yeval^1,\yinsp,r,r'))$, and $\cinsp =
  \EEnc(\PUBOK[\oid],\yinsp;r')$, for some random $r,r'$ and $n \ge 0$.
  % 
  Further, we build $G_1^0$ from $G_0^0$ by simulating the proof $\pi_0$. That
  is, in $G_1^0$, $\csig_0 = (\pi_0^s,\ceval,\cinsp)$, where $\pi^s_0 =
  \NIZKSim^{\RelSig}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
  \cinsp,\lbrace\PUBIK[\scid_{i,0}]\rbrace_{i\in[n]},\PUBOK[\oid]))$. By
  zero-knowledgeness of the NIZK for \RelSig, $G_1^0$ is indistinguishable from
  $G_0^0$.

  Similarly, we consider $G_0^1$ and $G_1^1$. That is, $G_0^1 = \ExpSigAnono$,
  where the challenge
  sent to the adversary is $(\csig_1,\yeval) \gets \Sign(\PRVUK[\cuid_1],
  \PUBOK[\oid],\CRED[\scid_1],\msg,\feval)$, where $\csig_1 = (\pi_1,
  \cinsp)$, with $\pi_1 = \NIZKProve^{\RelSig}(\NIZKcrs_{\Sign},
  (\msg,\feval,\yeval,
  \cinsp,\lbrace\PUBIK[\scid_{i,1}]\rbrace_{i\in[n]},\PUBOK[\oid]),
  (\PUBUK[\cuid_1],\PRVUK[\cuid_1],\lbrace (\scid_{i,1},\attrs_{i,1},
  \CRED[\scid_{i,1}]) \rbrace_{i\in[n]},\yeval^1,\yinsp,r,r'))$, and
  $\cinsp = \EEnc(\PUBOK[\oid],\yinsp;r')$, for random $r,r'$ and $n \ge 0$. As
  before, build $G_1^1$ from $G_0^1$, simulating $\pi_1$. That is, in $G_1^1$,
  $\csig_1 = (\pi_1^s,\ceval,\cinsp)$, where $\pi^s_1 =
  \NIZKSim^{\RelSig}(\NIZKcrs_{\Sign},\NIZKtrap,(\msg,\feval,\yeval,
  \cinsp,\lbrace\PUBIK[\scid_{i,1}]\rbrace_{i\in[n]},\PUBOK[\oid]))$. Again, by
  zero-knowledge of THE NIZK for \RelSig, $G_1^1$ is
  indistinguishable from $G_0^1$.

@@

  Next, we prove that, after zero-knowledge and simulation extractability of the
  NIZK for \RelSig, and blindness of \SBCM, no credential from an honest user
  can be extracted from the signature output by \adv, except with negligible
  probability.
  %
  The crucial observation is that, as in \cite{cl06} \CUASGen's \Sign algorithm
  produces a signature of knowledge for the relation defined by \RelSig
  That is, given $(x,w) \in \RelSig$, one can compare $x$ and $w$ to
  the public and private key of a signature algorithm, respectively. In \RelSig,
  $(\upk,\usk,\lbrace (\cid_i,\attrs_i,
  \cred_i)\rbrace_{i\in[n]},\yeval^1,\yinsp,r,r')$ is the private key ($w$), and
  $(\msg,\feval,\yeval^0,\cinsp,\lbrace \ipk_i \rbrace_{i\in[n]},\ek)$ is the
  public key ($x$).
  %
  From this, we prove that an adversary has only negligible probability to forge
  a signature as originating from an honest user without calling the \SIGN
  oracle. The strategy is similar to that in \cite[Theorem 2.1]{cl06}.

### 2022-10-06 prism-backend/research/gsac/introduction-paper.tex
Fixed some flaws. Still doing passes for minor checks.
Minor edits.

\paragraph{Utility at, and after, authentication time.} %
AC schemes target utility at authentication time. For instance, allowing
users to selectively disclose subsets of the attributes in their credentials.
Their real world applications are direct, e.g., to prove ``Over 18''-type of
claims. Indeed, the scientific research behind anonymous credentials is becoming
a foundational block of the technology some call ``anoncreds''%
\footnote{\url{https://hyperledger-indy.readthedocs.io/projects/sdk/en/latest/docs/design/002-anoncreds/README.html}. Last access, June 18th, 2022.},
the privacy-preserving cousin of W3C's Verifiable Credentials%
\footnote{\url{https://www.w3.org/TR/vc-data-model/}. Last access, June 18th,
  2022.}.

GS schemes enhance utility after authentication, allowing partial
re-identification like linking of signatures, or even full deanonymisation.
While actual applications of group signatures seem hard to find in the real
world, Direct Anonymous Attestation (DAA) \cite{bcc04,bl07,cdl16b} has been
deployed to millions of computing devices into what's called TPM (Trusted
Privacy Module)%
\footnote{\url{https://trustedcomputinggroup.org/resource/trusted-platform-module-tpm-summary/}. Last access, June 18th, 2022.}.
Indeed, DAA is a very close relative of group signatures, where the signer is
divided into two components (trusted and partially trusted), and signing
and verification are interactive.

@@

\paragraph{Generic construction.} %
We give \CUASGen, a generic construction of UAS based on well-known
building blocks, and prove its security. Despite its functional flexibility, our
construction is simple. Like many previous related schemes, credentials are
signatures over blocks of messages -- each message encoding a different
attribute. Users simultaneously leveraging multiple credentials need to prove
that they are bound to the same key. Utility information to be revealed at
signing time is output in plain text, and utility information extractable by
openers is encrypted under their public key -- in both cases, users prove
correct computation.

>>>>

\paragraph{Utility at, and after, authentication time.} %
AC schemes target utility at authentication time. For instance, allowing
users to selectively disclose subsets of the attributes in their credentials.
Their real world applications are direct, e.g., to prove ``Over 18''-type of
claims. Indeed, the scientific research behind anonymous credentials is becoming
a foundational block of the technology some call ``anoncreds''%
\footnote{\url{https://hyperledger-indy.readthedocs.io/projects/sdk/en/latest/docs/design/002-anoncreds/README.html}. Last access, October 6th, 2022.},
the privacy-preserving cousin of W3C's Verifiable Credentials%
\footnote{\url{https://www.w3.org/TR/vc-data-model/}. Last access, October 6th,
  2022.}.

GS schemes enhance utility after authentication, allowing partial
re-identification like linking of signatures, or even full deanonymisation.
While actual applications of group signatures seem hard to find in the real
world, Direct Anonymous Attestation (DAA) \cite{bcc04,bl07,cdl16b} has been
deployed to millions of computing devices into what's called TPM (Trusted
Privacy Module)%
\footnote{\url{https://trustedcomputinggroup.org/resource/trusted-platform-module-tpm-summary/}. Last access, October 6th, 2022.}.
Indeed, DAA is a very close relative of group signatures, where the signer is
divided into two components (trusted and partially trusted), and signing
and verification are interactive.

@@

\paragraph{Generic construction.} %
We give \CUASGen, a generic construction of UAS based on well-known
building blocks, and prove its security. Despite its functional flexibility, our
construction is simple. Like many related schemes, credentials are
signatures over blocks of messages -- each message encoding a different
attribute. Users simultaneously leveraging multiple credentials need to prove
that they are bound to the same key. Utility information to be revealed at
signing time is output in plain text, and utility information extractable by
openers is encrypted under their public key -- in both cases, users prove
correct computation.
